Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-04-01 paper.qmd
Added langevitour for MNIST data

<!--bin1 = 22, bin2 = 17, b = 374, non_empty = 140-->
```{r}
#| label: mnist-model-proj

@@

scaled_mnist_data_model <- scaled_mnist |>
  filter(type == "model") |>
  select(-type)

>>>>

<!--bin1 = 22, bin2 = 17, b = 374, non_empty = 140-->

```{r}
#| label: data-prep-mnist-model-proj

@@

scaled_mnist_data_model <- scaled_mnist |>
  filter(type == "model") |>
  select(-type)
```

data_mnist_cluster <- data_mnist |>
  select(-type) |>
  mutate(type = tsne_minst_scaled$cluster)

df_model_data_mnist_n <- bind_rows(data_mnist_cluster, df_b_mnist)

langevitour::langevitour(df_model_data_mnist_n[1:(length(df_model_data_mnist_n)-1)],
                         lineFrom = distance_df_small_edges_mnist$from,
                         lineTo = distance_df_small_edges_mnist$to,
                         group = factor(df_model_data_mnist_n$type,
                                        c("big_clust", "small_clust", "model")),
                         levelColors = c("#999999",'#ff7f00', "#000000"))
```

```{r}
#| label: mnist-model-proj
